### 2019-03-01 results.tex
mz - michael pass

The applications train a model on a random subset (80\%) of the data. Each then uses this model to predict the field from which each fruit originates for the remaining 20\%. To study the impact of random data split, we consider multiple (30 in our experiments) 80\%/20\% splits in our evaluation.
\subsection{Empirical Methodology}

@@

Seneca deploys the applications automatically over AWS Lambda
and extracts execution time and memory use from 
AWS CloudWatch~\cite{ref:awscloudwatch} logs.
We compute monetary cost using the AWS Lambda pricing model~\cite{ref:pricing}.
Each function downloads the training/testing dataset 
of the application from AWS S3 upon function invocation. 
We do not consider the cost of dataset storage 
in our cost computations (it is very small, under X cents).
%\footnote{\url{https://aws.amazon.com/cloudwatch/}}
%\footnote{\url{https://aws.amazon.com/lambda/pricing/}}
We also evaluate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the applications using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size. Even though \texttt{maximum memory used} reported by AWS CloudWatch can fluctuate, we 
have verified that the optimized allocated memory is sufficient for all 
hyperparameter configurations to complete successfully.  We have also verified
that the memory requirements across hyperparemeter settings do not vary 
significantly. We plan to consider applications for which hyperparameter settings require
different maximum memory sizes as part of future work.

>>>>

The applications train a model on a random subset (80\%) of the data. Each then uses this model to predict the field from which each fruit originates for the remaining 20\%. To study the impact of random data split, we consider multiple 80\%/20\% splits in our evaluation.
\subsection{Empirical Methodology}

@@

Seneca deploys the applications automatically over AWS Lambda
and extracts execution time and memory use from 
AWS CloudWatch~\cite{ref:awscloudwatch} logs.
We compute monetary cost using the AWS Lambda pricing model~\cite{ref:pricing}.
Each function downloads the training/testing dataset 
of the application from AWS S3 upon function invocation. 
We do not consider the cost of dataset storage 
in our cost computations, because it is very small. For XGBoost that makes most S3 requests among others, the cost is under 2.5 cents for storage and request combined in a month.
%\footnote{\url{https://aws.amazon.com/cloudwatch/}}
%\footnote{\url{https://aws.amazon.com/lambda/pricing/}}
We also evaluate Seneca's automatic memory optimization capabilities.  To
do so we compare the execution performance and cost of the applications using
the maximum allocatable memory size to the performance and cost when run with
Seneca's automatically determined memory size. Even though \texttt{maximum memory used} reported by AWS CloudWatch can fluctuate, we 
have verified that the optimized allocated memory is sufficient for all 
hyperparameter configurations to complete successfully.  We have also verified
that the memory requirements across hyperparemeter settings do not vary 
significantly. We plan to consider applications for which hyperparameter settings require
different maximum memory sizes as part of future work.
